### 2019-04-19 chapters/4-discussion.tex
shape

>>>>

In addition to texture features, shape descriptors might provide information
useful for Gleason score characterization \citep{Hoeks2011}. However, we
decided to leave them out of this study and focus on texture features only.
Including shape features would have required to treat lesions of different
prostate regions differently, since lesions in peripheral zone might spread
differently than lesions in central/transitional zone.
